\chapter{Baaj Temple}

\begin{enumerate}
    \item Hold \Cancel, Down-Left to talk to Jecht
    \item Swim around rock and to temple
    \item Buffer down and right, hold \Cancel
\end{enumerate}
\begin{battle}{Sahagins and Geosgaeno}
    \begin{itemize}
        \item Attack the two Sahagins until dead
        \item Defend until end
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Buffer Turbo: Heal \tidus\ with Potions
    \item Go to options ($\uparrow \uparrow$), switch cursor to memory, aeons to short
    \item Up to Door, buffer down+left and go through door. Pickup flint and exit.
    \item Go north and through door. Climb steps to withered bouquet. Go back to the fire in the center.
\end{enumerate}
\begin{battle}[1500]{Klikk}
    \begin{itemize}
        \tidusf Attack x6, Potion once \tidus\ has less than 227 HP
        \rikkuf Grenade x1, Steal x2 Grenades Total, Attack (need at least 6 Grenades for Tros)
        \tidusf Attack
        \item Potion if \tidus\ has less than 114 HP
        \item Continue until dead
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Down to \rikku\
    \item Hold \Cancel, down, left. Use circle and move forward.
\end{enumerate}
\begin{encounters}
    \begin{itemize}
        \item Piranha:
        \begin{itemize}
            \item Steal Grenades with \rikku\ and Attack with \tidus
        \end{itemize}
    \end{itemize}
\end{encounters}
\begin{enumerate}[resume]
    \item Swim to \save, swim forward. Circle and right across the station.
\end{enumerate}
\begin{battle}{Piranha}
    \begin{itemize}
        \rikkuf Steal Grenades from each set
        \tidusf Attack
        \item Keep track of \rikku\ HP
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \cs, swim down, swim left. Heal with Potions if \rikku\ is below 250 HP.
\end{enumerate}
\begin{battle}[2200]{Tros}
    \begin{itemize}
        \rikkuf Steal if you had less than 6 grenades
        \rikkuf Grenade x6
        \tidusf Attack x2, Standby otherwise
        \enemyf Charge hits for 180
    \end{itemize}
    Guaranteed 2 Power Spheres, Overkill gives +2 Power Spheres
\end{battle}
\begin{enumerate}[resume]
    \item Swim up to the next screen. Follow red arrow to the right
    \item Talk to \rikku.
\end{enumerate}
