\chapter{Besaid}

\begin{enumerate}
    \item Swim to the beach. Walk up to \wakka, walk down to next screen.
    \item Walk Down+Right to next screen, Down+Right into Right again, Up to \wakka.
    \item Swim in the Lagoon. Watch out for invisible wall at the end.
\end{enumerate}
\begin{encounters}
    \begin{itemize}
        \item Piranhas:
        \begin{itemize}
            \item Attack if 2 groups, or 3 if preempt
            \item Otherwise run away
            \item Keep track of \tidus\ level
        \end{itemize}
    \end{itemize}
\end{encounters}
\begin{enumerate}[resume]
    \item Walk to temple until \cs\ is removed
    \item Walk to \wakka\ tent (middle right), talk to him and \nth{1} option
    \item Walk to temple
\end{enumerate}
\begin{trial}
    \begin{itemize}
        \item Touch the wall at the end
        \item Touch the wall on the right
        \item Go down the steps and pickup the sphere from the wall
        \item Go down the steps and place the sphere in the door
        \item Go down the corridor past the first pedestal
        \item Touch the wall opposite the second pedestal to open the hidden room
        \item Pickup the sphere in the hidden room, place it on the second pedestal
        \item Push the pedestal to complete the trials
    \end{itemize}
\end{trial}
\begin{enumerate}[resume]
    \item Walk down to Besaid Center, name \valefor
    \item Walk to \yuna, talk to \wakka and \nth{1} option, \sd\ on the dream docks
    \item Walk out of tent, leave village
    \item \turbo\ through forced encounters (guaranteed 1 Power Sphere, Overkill on Dingo gives +1 Power Sphere)
    \item Go up after statue scene
\end{enumerate}
\begin{spheregrid}
    \begin{itemize}
        \item \textit{If \tidus\ has 3 levels:}
        \begin{itemize}
            \item Move $\leftarrow$ to Def Node
            \item Get Cheer, Str +1 (Careful, cursor is on Def+1 by default)
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/tiduscheer}
    \end{itemize}
\end{spheregrid}
\begin{battle}[750]{Kimahri}
    Each Attack does average of 125, count damage compared to average to know if you need to Potion or not.
    If you did the above sphere grid already, 6 Attacks will always kill.
    \begin{itemize}
        \tidusf Attack x5 (hold \turbo)
        \item \textit{If the Attacks did at least 7 damage over average:}
        \begin{itemize}
            \tidusf Attack
        \end{itemize}
        \item \textit{If \tidus\ has less than 178 HP:}
        \begin{itemize}
            \tidusf Potion
        \end{itemize}
        \tidusf Attack x1-2
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Continue running
\end{enumerate}
\begin{battle}{Garuda}
    \begin{itemize}
        \summon{\valefor}
        \valeforf Thunder x6 to build \od\ (\turbo\ break after Thunder [0:50])
    \end{itemize}
    Guaranteed 1 Power Sphere
\end{battle}
\begin{enumerate}[resume]
    \item \formation{\tidus}{\yuna}{\lulu} (Get \wakka\ out)
    \item If you didn't do the above sphere grid yet, do it now (only get Cheer if Tidus has 2 levels).
\end{enumerate}
\begin{battle}{Garuda}
    \begin{itemize}
        \item Flee using the Escape Command
    \end{itemize}
\end{battle}
\begin{encounters}
    \begin{itemize}
        \item Dingo: \tidus\ Attack
        \item Condor: \wakka\ Attack
        \item Water Flan: \lulu\ Thunder
    \end{itemize}
    Guaranteed 1 Power Sphere, Overkill on Dingo gives +1 Power Sphere.
\end{encounters}
\begin{enumerate}[resume]
    \item At Besaid Beach \save
    \item Talk to the guy in red shorts for 400 Gil, go onto the boat
\end{enumerate}
\begin{spheregrid}
    \begin{itemize}
        \item \textit{If not done before:}
        \begin{itemize}
            \item Move $\leftarrow$ to Def Node
            \item Get Cheer, Str +1 (Careful, cursor is on Def+1 by default)
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/tiduscheer}
    \end{itemize}
\end{spheregrid}
\winnp\lossnp\bothnp
