\chapter{Mt. Gagazet}
\begin{enumerate}
    \item If \kimahri\ is not full, \save
\end{enumerate}
\begin{battle}{Biran and Yenke}
    \begin{itemize}
        \kimahrif Steal from Biran
        \enemyf Biran Bulldoze
        \kimahrif Gem Yenke
        \kimahrif Gem Biran
    \end{itemize}
    Pay attention to your drops, they affect \yuna's sphere grid below.
\end{battle}
\begin{enumerate}[resume]
    \item The drop from the previous fight will give be one of the following:
    \begin{itemize}
        \item \textbf{4 Return Spheres}
        \item \textbf{2 Return Spheres and 2 Friend Spheres}
        \item \textbf{0 Return Spheres and 4 Friend Spheres}
    \end{itemize}
    \item These three branching paths will from now on be referred to by the number of \textbf{Return Spheres} that dropped.
    \item Do the \lulu\ Grid below first, then one of the three Grids depending on the drop from the previous fight.
\end{enumerate}
\begin{spheregrid}[Lulu]
    \begin{itemize}
        \luluf
        \begin{itemize}
            \item Move $\uparrow\uparrow$ to Fire
            \item Level 2 Key Sphere (\textbf{not} Lvl.1)
            \item Move $\downarrow x9$ to center MDef node
            \item Level 3 Key Sphere
            \item Move $\searrow\searrow$ to middle Str node
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/lulu_grid}
    \end{itemize}
\end{spheregrid}
\begin{spheregrid}[\textbf{4 Return Spheres}]
    \begin{itemize}
        \blitzballdetermination[true]{%
            \yunaf Use Return Sphere to Str+4 Node above
            \yunaf Move to the empty node $\leftarrow\downarrow$ where Tidus is
            \yunaf Str+4, Agi+2
            \item \sggraphics{.7}{.4}{graphics/4_returns_1}
        }{%
            \yunaf Use Return Sphere to Str+4 Node $\leftarrow$
            \yunaf Move to the empty node $\rightarrow\rightarrow\rightarrow$
            \yunaf Str+4, Def+3
            \item \sggraphics{.7}{.4}{graphics/loss_4_returns_1}
        }
        \tidusf Move to Armor Break $\rightarrow x3, \downarrow x5$ next to the center node
        \tidusf Armor Break
        \item \sggraphics{.7}{.4}{graphics/Tidus armor break 4 returns}
    \end{itemize}
\end{spheregrid}
\begin{spheregrid}[\textbf{2 Return Spheres}]
    \begin{itemize}
        \blitzballdetermination[true]{%
            \yunaf Move to the empty node $\leftarrow$ where Tidus is
            \yunaf Str+4, Agi+2
            \item \sggraphics{.7}{.4}{graphics/2_and_2-1}
        }{%
            \yunaf Move to the empty node $\rightarrow\rightarrow$
            \yunaf Str+4, Def+3
            \item \sggraphics{.7}{.4}{graphics/loss_2_and_2-1}
        }
        \yunaf Friend Sphere to \lulu\ $\downarrow\downarrow$
        \yunaf Str+4, Str+4
        \luluf Move $\nearrow\uparrow\uparrow$ to NE Str node
        \yunaf Friend Sphere to \lulu
        \yunaf Str+3, Agi+4, Agi+4
        \item \sggraphics{.7}{.4}{graphics/2_and_2}
        \tidusf \textit{skip grid movements:} Return Sphere $\downarrow\searrow\searrow$ (or Hold $\searrow$) to Str+4 near Armor Break
        \tidusf Move $\nwarrow\leftarrow$ or $\leftarrow x3$
        \tidusf \textit{Alternative:} Move to Armor Break $\rightarrow x3, \downarrow x5$ next to the center node
        \tidusf Armor Break
        \item \sggraphics{.7}{.4}{graphics/Tidus armor break 2 returns}
    \end{itemize}
\end{spheregrid}
\begin{spheregrid}[\textbf{0 Return Spheres}]
    \begin{itemize}
        \blitzballdetermination[true]{%
            \tidusf Move to Str+4 by Mental Break $\rightarrow x3, \downarrow, \rightarrow x3$
            \item \sggraphics{.7}{.4}{graphics/0_returns_pt2}
            \yunaf Move to the empty node $\leftarrow$
            \yunaf Str+4, Agi+2
            \item \sggraphics{.7}{.4}{graphics/2_and_2-1}
        }{%
            \tidusf Move to Armor Break $\rightarrow x3, \downarrow x6$
            \tidusf Armor Break
            \tidusf Move to HP $\rightarrow\rightarrow\downarrow$
            \yunaf Move to the empty node $\rightarrow\rightarrow$
            \yunaf Str+4, Def+3
            \item \sggraphics{.7}{.4}{graphics/loss_2_and_2-1}
        }
        \yunaf Friend Sphere to \tidus
        \yunaf Str+4
        \item Friend Sphere to Lulu twice like described \textbf{in the 2 Return Sphere Menu}
        \kimahrif Move $\swarrow x2$
        \yunaf Friend to \kimahri\ $\downarrow$
        \yunaf Agi+4
        \item \sggraphics{.7}{.4}{graphics/post_BY_0_returns}
        \blitzballdetermination[true]{%
            \tidusf Move $\nwarrow\leftarrow$ or $\leftarrow x3$
            \tidusf Armor Break
            \ifthenelse{\equal{\blitzresult}{both}}{%
                \item \sggraphics{.7}{.2}{graphics/Tidus armor break 0 returns}
            }{%
                \item \sggraphics{.7}{.4}{graphics/Tidus armor break 0 returns}
            }
        }{}
    \end{itemize}
\end{spheregrid}
\begin{enumerate}[resume]
    \item \textit{If you got \textbf{4 Return Spheres}}, Customize:
    \begin{itemize}
        \auronf Shimmering Blade $\rightarrow$ First Strike
        \yunaf Staff $\rightarrow$ First Strike
    \end{itemize}
    \item \textit{If you got \textbf{2 Return Spheres}:}, Customize:
    \begin{itemize}
        \yunaf Staff $\rightarrow$ First Strike
    \end{itemize}
    \item \textit{If you need need to charge \rikku's \od} \formation{\tidus}{\rikku}{\auron}, otherwise \formation{\tidus}{\kimahri}{\wakka}.
\end{enumerate}
\begin{enumerate}[resume]
    \item Walk up, avoid the gravestones.
    \item Have either:
    \begin{itemize}
        \item A Silence Grenade
        \item \rikku's \od\ (Add her to Party, on full mech encounter, Steal from Leader with \rikku, escape with the others)
    \end{itemize}
    \item Follow the path around.
    \item \textit{If you had 2 or 4 \textbf{Return Spheres}} \formation{\tidus}{\yuna}{\auron}, otherwise \formation{\tidus}{\kimahri}{\wakka}
\end{enumerate}
\begin{battle}[70000]{Seymour Flux}
    \begin{itemize}
        \item \textit{If you had 4 \textbf{Return Spheres}:}
        \begin{itemize}
            \yunaf Attack
            \tidusf Haste \yuna
            \switch{\auron}{\rikku}
            \rikkuf Use Silence Grenade or  \od\ HP Sphere + Grenade
            \summon{\bahamut}
            \bahamutf \textit{If you used a Silence Grenade} Impulse, otherwise Attack
            \enemyf Banishes Bahamut
            \yunaf Attack
            \tidusf \textit{If you used a Silence Grenade} Attack once, otherwise Defend
            \rikkuf Defend
            \item Finishing Seymour with \yuna\ will be an Overkill, otherwise it's not. Keep track of this.
        \end{itemize}
        \item \textit{If you had 2 \textbf{Return Spheres}:}
        \begin{itemize}
            \yunaf Attack
            \tidusf Haste \yuna
            \summon{\bahamut}
            \bahamutf Impulse
        \end{itemize}
        \item \textit{If you had 0 \textbf{Return Spheres}:}
        \begin{itemize}
            \switch{\tidus}{\yuna}
            \summon{\bahamut}
            \bahamutf Attack
        \end{itemize}
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \formation{\tidus}{\kimahri}{\auron}
    \item \save\ if \bahamut\ was banished, Walk to the next screen
    \item Walk up to \tidus\ House, go into the center, walk up to the next screens
    \item Go down the left path into the water, swim up. Go up the steps, play the minigame, return to the previous screen.
    \item Throw at the \nth{3} narrowing of the \nth{2} wall
    \item Sphere farming check, at this point you need
    \begin{itemize}
        \item \textit{If you had 4 Return Spheres}:
        \begin{itemize}
            \item 4 Power Spheres
            \item 5 Speed Spheres
        \end{itemize}
        \item \textit{If you had 2 Return Spheres}:
        \begin{itemize}
            \item 1 Power Sphere
            \item 5 Speed Spheres
        \end{itemize}
        \item \textit{If you had 0 Return Spheres}:
        \begin{itemize}
            \item 2 Speed Spheres (no more Power Spheres)
        \end{itemize}
        \item \tidus\ can attack Splashers in formation without any other fiends for Power Spheres
        \item Other missing Spheres can be distilled inside Sin
    \end{itemize}
    \item Return to Save Sphere, go up and left, then go down the right path, swim up into the next screen.
    \item Complete the minigame, \rikku\ Green, \tidus\ Blue, \wakka\ Red. Return.
    \item Go up left path, \save\ if \bahamut\ was banished and you didn't touch one earlier.
    \item \formation{\tidus}{\yuna}{\wakka}. Go onto the next screen.
\end{enumerate}
\begin{battle}[40000]{Sanctuary Keeper}
    \begin{itemize}
        \item \textit{If you got 2 or 4 \textbf{Return Spheres}:}
        \begin{itemize}
            \yunaf Defend
            \tidusf Armor Break
        \end{itemize}
        \item \textit{If 0 \textbf{Returns Spheres}:}
        \begin{itemize}
            \tidusf Defend
        \end{itemize}
        \summon{\bahamut}
        \bahamutf Attack
    \end{itemize}
\end{battle}
\winnpsingle\lossnpsingle
